Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

As there is no standard way to formulate constraints, 
semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
since constraint transformations avoid the necessity to understand several constraint languages.

We provide a validation environment \footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages 
i.e., validation is independent from the used constraint language (see section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main contributions of this paper are:
(1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (section \ref{sec:vocabulary}),
(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \ref{sec:transformations}), and
(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

A \emph{simple constraint} holds for all individuals of a \emph{context class}.
Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):

@@

For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
\emph{Object Property Paths} (\emph{R-55}; also called \emph{complex role inclusion axioms} in \emph{DL})
express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
\begin{DL}
authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre 
\end{DL}
Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
and the property \emph{authorOfGenre} is on the right side:

@@

\begin{ex}
ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
    owl:onDatatype xsd:string ; 
    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]" ])] .
\end{ex} 
The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype. %\er{Why start from second and then first? Also better we say "owl axiom" when we talk axiom of owl, to prevent ambiguity.}\tb{resolved}
The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
The datatype {\em ISBN} can be used just like any other datatype like in the \emph{universal restriction} above.
%There are multiple use cases associated with the requirement to match literals according to given patterns (\emph{Literal Pattern Matching}\footnote{Corresponds to \emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
%The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
%The universal restriction can be represented in DL:
%\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
%The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
%
%\begin{ex}
%RegistryNumber
    %a rdfs:Datatype ; owl:equivalentClass [ a rdfs:Datatype ;
        %owl:onDatatype xsd:string ;
        %owl:withRestrictions ( [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
%\end{ex}
%The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
%The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
%The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the regular expression causing constraint violations for triples which do not not match. 
%\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
%but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
In table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}:

@@

As the \emph{The-Great-Gatsby} is a \emph{publication} (\ms{rdf:type(The-Great-Gatsby, Publication)}) having an \emph{ISBN} number (\ms{isbn(The-Great-Gatsby, '978-0241965672')}) and a \emph{title} (\ms{title(The-Great-Gatsby, 'The Great Gatsby')}) and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
%\begin{DL}
%rdf:type(BElannaTorres,Half-Klingon) \\
%klingonMother(BElannaTorres,Miral) \\
%klingonMother(BElannaTorres,JohnTorres)
%\end{DL}
The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:

@@

%Even though, tools may generate \emph{generic constraints} automatically, this 
\emph{Complex constraints} are composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:simplified-complex-constraints}).

@@

Almost 15 percent of all constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).

There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
Such axioms, however, are just syntactic sugar - 
all role characteristics can be expressed using the basic features of \emph{DL}.
The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
\begin{DL}
\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
\end{DL}
When mapped to the \emph{RDF-CV} (see table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):

@@

When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see table \ref{tab:irreflexive-object-properties-as-simple-constraints}):

@@

The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
For instance, \emph{Books} are uniquely identified by their \emph{ISBN} number, that is, the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see table \ref{tab:primary-key-properties-as-complex-constraints}):

@@

\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
A key can be a datatype, an object property, or a chain of properties.
For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
\emph{DL} is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).

@@

The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}).
Then, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ReSh})$}, \emph{$m_3(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).

>>>>

As there is no standard way to formulate constraints, 
semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
since constraint transformations avoid the necessity to understand several constraint languages.

We provide a validation environment \footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages 
i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main contributions of this paper are:
(1) we provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}),
(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (Section \ref{sec:vocabulary}),
(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}), and
(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

A \emph{simple constraint} holds for all individuals of a \emph{context class}.
Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see Table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):

@@

For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
\emph{Object Property Paths} (\emph{R-55}; also called \emph{complex role inclusion axioms} in \emph{DL})
express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
\begin{DL}
authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre 
\end{DL}
Thus, when mapped to the \emph{RDF-CV} (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
and the property \emph{authorOfGenre} is on the right side:

@@

\begin{ex}
ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
    owl:onDatatype xsd:string ; 
    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]" ])] .
\end{ex} 
The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype. %\er{Why start from second and then first? Also better we say "owl axiom" when we talk axiom of owl, to prevent ambiguity.}\tb{resolved}
The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
The datatype {\em ISBN} can be used just like any other datatype like in the \emph{universal restriction} above.
%There are multiple use cases associated with the requirement to match literals according to given patterns (\emph{Literal Pattern Matching}\footnote{Corresponds to \emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
%The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
%The universal restriction can be represented in DL:
%\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
%The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
%
%\begin{ex}
%RegistryNumber
    %a rdfs:Datatype ; owl:equivalentClass [ a rdfs:Datatype ;
        %owl:onDatatype xsd:string ;
        %owl:withRestrictions ( [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
%\end{ex}
%The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
%The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
%The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the regular expression causing constraint violations for triples which do not not match. 
%\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
%but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
In Table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}:

@@

As the \emph{The-Great-Gatsby} is a \emph{publication} (\ms{rdf:type(The-Great-Gatsby, Publication)}) having an \emph{ISBN} number (\ms{isbn(The-Great-Gatsby, '978-0241965672')}) and a \emph{title} (\ms{title(The-Great-Gatsby, 'The Great Gatsby')}) and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
%\begin{DL}
%rdf:type(BElannaTorres,Half-Klingon) \\
%klingonMother(BElannaTorres,Miral) \\
%klingonMother(BElannaTorres,JohnTorres)
%\end{DL}
The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:

@@

%Even though, tools may generate \emph{generic constraints} automatically, this 
\emph{Complex constraints} are composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).

@@

Almost 15 percent of all constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see Section \ref{sec:evaluation}).

There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
Such axioms, however, are just syntactic sugar - 
all role characteristics can be expressed using the basic features of \emph{DL}.
The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
\begin{DL}
\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
\end{DL}
When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):

@@

When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):

@@

The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
For instance, \emph{Books} are uniquely identified by their \emph{ISBN} number, that is, the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see Table \ref{tab:primary-key-properties-as-complex-constraints}):

@@

\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
A key can be a datatype, an object property, or a chain of properties.
For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
\emph{DL} is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see Table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).

@@

The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see Table \ref{tab:existential-quantification-as-simple-constraints}).
Then, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ReSh})$}, \emph{$m_3(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).
